Data Management for LSST Special Programs

### 2024-03-27 sec_proc.tex
minor updates

\textbf{Potential issues with Prompt processing for untiled sequences from Special Programs.}
There are two potential issues with Prompt processing for DDFs, or any mini-survey 
that obtains a sequence of untiled images (images at the same pointing or which overlap).
For example, a DDF which obtains a hour-long series of about a hundred images at the same coordinates,
every few nights for a few months.

@@

In short, \emph{possible} means that original or reconfigured versions of the LSST
Science Pipelines can be used , and \emph{necessary} means the primary science goal for Special Program
could not be met without the data products produced by the Special Processing.

@@

The interpretations of possible and necessary, and the scope of Special Processing,
are ultimately left to the discretion of Rubin Data Management in Operations.

Specific examples are provided only to illustrate this interpretation of possible and necessary.
These examples do not place limits on what Special Processing might be done.

@@

\item \textbf{Possible and necessary:}
in order to detect high-redshift (faint) galaxies in the DDFs,
Rubin Data Management uses the LSST Science Pipelines to deeply
coadd images for each field, and store the results of source
detection and characterization in unique and separate tables that
are included in the annual data release.

\item \textbf{Possible but not necessary:}
a time-domain mini-survey that uses standard visits \emph{could}
have separate difference-image analysis object and source catalogs
generated, but this is not necessary as the science goals for the
mini-survey can be met by processing its data with standard Prompt
Processing, and ensuring the data is properly labeled.

@@

Consider a Special Program in which a special region of sky is observed with standard
visits but a a special strategy or cadence which is significantly distinct from the Main Survey
observing modes, and lasts for a limited amount of time.
For example, a short-term survey of the Magellanic Clouds, with dual primary science
goals in time-domain and static-sky science.

In cases like this, a set of unique and separate data products with the same formats as the 
time-domain DIA and static-sky data products described in Section~\ref{sssec:proc_reg_dr}
could be created with Special Processing, if they are necessary 
(i.e., Special Processing and data products will not be made if they will be redundant
with the products of Standard Processing).
They might be released with an annual data release or on an intermediate timescale, e.g.,
within six months of the conclusion of the mini-survey observations.

@@

Science goals that require data products which are not possible to create with 
the original or reconfigured versions of the LSST Science Pipelines, 
and/or for which new algorithmic development or significant computational resources 
are needed, will require user processing and user-generated data products.
As described above, custom coadds (e.g., weekly, monthly) are also left to users 
to generate, as required by their specific science goals.

@@

\textbf{Adopting user code or data products --}
It is expected that some User-Generated pipelines and data products 
might be ``adopted" or ``federated" into the LSST Science Pipelines and the Prompt 
and Data Release data products.
Details regarding this are to be provided elsewhere.

>>>>

\textbf{Potential issues with Prompt processing for untiled (deep drilling) sequences.}
There are two potential issues with Prompt processing for DDFs, or any mini-survey 
that obtains a sequence of untiled images (images at the same pointing or which overlap).
For example, a DDF which obtains a hour-long series of about a hundred images at the same coordinates,
every few nights for a few months.

@@

There are several caveats and constraints on the definition of
"possible and necessary" in Section~\ref{ssec:sci_sproc}, but
in short \emph{possible} means that original or reconfigured versions of the LSST
Science Pipelines can be used and \emph{necessary} means the \emph{primary} science goal
of the Special Program could not otherwise be met.

@@

The scope of Special Processing is at the discretion of Rubin Data Management.
Specific examples are provided here as illustration.
These examples do not place limits on what Special Processing might be done.

@@

\item \textbf{Possible and necessary:}
in order to detect high-redshift (faint) galaxies in the DDFs,
Rubin Data Management uses the LSST Science Pipelines to deeply
coadd images for each field, and store the results of object
detection and characterization in unique and separate tables that
are included in the annual data release.

\item \textbf{Possible but not necessary:}
a time-domain mini-survey that uses standard visits \emph{could}
have separate difference-image analysis object and source catalogs
generated, but this is not necessary as the science goals for the
mini-survey can be met by processing its data with standard Prompt
Processing and ensuring the data is properly labeled.

@@

Consider a Special Program in which a special region of sky is observed with standard
visits but a pecial strategy or cadence which is significantly distinct from the Main Survey
observing modes, and lasts for a limited amount of time.
For example, a short-term survey of the Magellanic Clouds, with dual primary science
goals in time-domain and static-sky science.

In cases like this, a set of unique and separate data products with the same formats as the 
time-domain DIA and static-sky data products described in Section~\ref{sssec:proc_reg_dr}
could be created with Special Processing, if they are necessary.
Special Processing and data products will not be made if they will be redundant
with the products of Standard Processing.
They might be released with an annual data release or on an intermediate timescale, e.g.,
within six months of the conclusion of the mini-survey observations.

@@

Science goals that require data products which are not possible to create with 
the original or reconfigured versions of the LSST Science Pipelines, 
and/or for which new algorithmic development or significant computational resources 
are needed, will require User-Generated Processing and user-generated data products.
As described above, custom coadds (e.g., weekly, monthly) are also left to users 
to generate, as required by their specific science goals.

@@

\textbf{Adopting user code or data products --}
It is expected that some User-Generated pipelines and data products 
might be ``adopted" or ``federated" into the LSST Science Pipelines and the Prompt 
and Data Release data products.
Guidelines for User-Generated Processing, and for user-generated data products
that can be federated with the Rubin-product data products (i.e., joinable tables),
is forthcoming.
